Inference methods comparison for the simplified Naomi model using maximum mean discrepancy

### 2025-08-05 src/naomi-simple_mmd/mmd.Rmd
Run MMD

```{r}
stopifnot(names(tmb$fit$sample) == names(aghq$quad$sample))
stopifnot(names(tmb$fit$sample) == names(tmbstan$mcmc$sample))
```

@@

#' Keep only the final 1000 samples from tmbstan
tmbstan_samples <- tmbstan_samples[, 4001:5000]

>>>>

```{r}
stopifnot(names(tmb$fit$sample) == names(aghq$quad$sample))
stopifnot(setequal(names(tmb$fit$sample), names(tmbstan$mcmc$sample)))
```

@@

#' Thin down to 1000 samples from tmbstan
tmbstan_samples <- tmbstan_samples[, seq(from = 1, to = ncol(tmbstan_samples), length.out = 1000)]
